\documentclass[12pt,a4paper]{report}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{Lenna X. Peterson}
\title{Bayesian Probabilities}
\begin{document}

\maketitle

\begin{equation}
P(E) = P(H,E) + P(\neg H, E)
\end{equation}

\begin{enumerate}
\item
	\begin{itemize}
		\item The probability of the evidence is equal to the probability of a true positive and the probability of a false positive.
		\item The chance of a positive test result is equal to the probability of a true positive and the probability of a false positive.
	\end{itemize}
\begin{equation}
P(E|H) = \frac{P(H,E)}{P(H)}
\end{equation}
\item 
	\begin{itemize}
		\item  The sensitivity is equal to the probability of a true positive divided by the probability of the hypothesis.
		\item The probability of a positive test result given cancer is equal to the probability of a true positive divided by the probability of cancer.
	\end{itemize}

\begin{align}
P(H|E) &= \frac{P(H,E)}{P(E)} \\
&= \frac{P(E|H)}{P(E)} \times P(H) \\
P(H) &: \; \text{Prior probability} \nonumber \\
P(H|E) &: \; \text{Posterior probability} \nonumber
\end{align}
\item 
	\begin{itemize} 
		\item The probability of the hypothesis given the evidence is equal to the probability of a true positive divided by the probability of the evidence. 
		\item The probability of having cancer given a positive test result is equal to the probability of a true positive divided by the probability of a positive test result.
	\end{itemize}
\item 
	\begin{itemize} 
		\item The probability of the hypothesis given the evidence is equal to the sensitivity divided by the probability of the evidence times the probability of the hypothesis.

		\item The posterior probability is equal to the prior probability modified by the sensitivity divided by the probability of the evidence.

		\item The probability of having cancer given a positive test result is equal to the sensitivity divided by the probability of a positive test result. times the probability of cancer
	\end{itemize}

\end{enumerate}

\end{document}